Data Exploration: IUCN and AquaMaps

### 2015-11-18 data_explore.Rmd
update data_explore to plot new graphs; show regressions; etc

### theme for species range maps - based on generic plot theme
ggtheme_map <- ggtheme_plot +
  theme(axis.text = element_blank())

@@

###(2) Looking at the total difference in area (km^2) for each species range map in both datasets

@@

####Now looking across all species, here is the breakdown of how much overlap there is between the two datasets

@@

Split up by species - not sure if this is useful or not
```{r, echo = FALSE, message = FALSE, warning = FALSE}

@@

@@

@@

@@

@@

@@

``` {r examine_spp_gp_quartiles}

@@

>>>>

### theme for species range maps - based on generic plot theme
ggtheme_map <- ggtheme_plot +
  theme(axis.text = element_blank()) +       
  scale_x_continuous(breaks = seq(-180, 180, by = 30), expand = c(0, 2)) +
  scale_y_continuous(breaks = seq( -90,  90, by = 30), expand = c(0, 2))

@@

###(2) Looking at the total difference in area (km^2^) for each species range map in both datasets

@@

#### Now looking across all species, here is the breakdown of how much overlap there is between the two datasets

@@

Split up by species groups

```{r, echo = FALSE, message = FALSE, warning = FALSE}

@@

summary(lm(total_area ~ sm_perc, spp_list))

@@

lm_eqn2 <- function(df){
  m  <- lm(area_ratio ~ sm_perc, spp_list)
  eq <- substitute(italic('y') == a + b %.% italic('x')*","~~italic(r)^2~"="~r2, 
        list(a  = format(coef(m)[1], digits = 2), 
             b  = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq))             
}

@@

scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap + 
  geom_text(x = 15, y = 1, label = lm_eqn2(spp_list), parse = TRUE, color = 'tomato2')

@@

scatter_arearatio_vs_overlap2 <- scatter_arearatio_vs_overlap2 + 
  geom_text(x = 15, y = 1, label = lm_eqn2(spp_list), parse = TRUE, color = 'grey30')

@@

summary(lm(area_ratio ~ sm_perc, spp_list))

@@

``` {r examine_spp_gp_quartiles, echo = FALSE}

@@

print(barchart_spp_gp_quads)
ggsave(plot = barchart_spp_gp_quads,
       filename = 'figures/barchart_spp_gp_quads.png',
       width = 6, height = 4)
